Manuscript

### 2021-08-06 Manuscript/Manuscript_old.Rmd
manuscript first draft

### Second search session

>>>>

### Second search session
The model trained on the last review task record was used to create new, data-driven, search queries to collect more results missed by the first batch of queries. As described in the methods, 2 slightly different query-generation algorithms were used and to both resulting string we added a further constrain to focus the results on "antimicrobial drug resistance" and "healthcare associated infections".
